NFC and burnout in teachers - A replication and extension study

### 2021-10-28 Manuscript/Manuscript.Rmd
completed description of DRR results

Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout.
The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of `r round(ncs_parcels$summed.difference, digits = 3)`.
The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
Standardized path coefficients of the demand-resource model are illustrated in **Figure**.
The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which was violated here.
This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
NFC showed no direct association with the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).

>>>>

Next we looked at how different ratios of subjective demands and resources affect the association of NFC and burnout.
The parcelling procedure for the indicators of the latent factor NFC resulted in four parcels with a summed difference in average loadings of `r round(ncs_parcels$summed.difference, digits = 3)`.
The first parcel contained item `r ncs_parcels$items[1,1]`, `r ncs_parcels$items[2,1]`, `r ncs_parcels$items[3,1]`, and `r ncs_parcels$items[4,1]`, the second parcel item `r ncs_parcels$items[1,2]`, `r ncs_parcels$items[2,2]`, `r ncs_parcels$items[3,2]`, and `r ncs_parcels$items[4,2]`, the third parcel item `r ncs_parcels$items[1,3]`, `r ncs_parcels$items[2,3]`, `r ncs_parcels$items[3,3]`, and `r ncs_parcels$items[4,3]`, and the fourth parcel item `r ncs_parcels$items[1,4]`, `r ncs_parcels$items[2,4]`, `r ncs_parcels$items[3,4]`, and `r ncs_parcels$items[4,4]`.
Standardized path coefficients of the demand-resource model are illustrated in **Figure**.
The robust Chi-square statistic of $\chi^2 = $`r round(fit2@test[["yuan.bentler.mplus"]]$stat, digits = 2)` ($p < .001$) did not indicate good model fit.
However, since it was in the range of `r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)`$*df < \chi^2 < $`r round(fit2@test[["yuan.bentler.mplus"]]$stat/fit2@test[["yuan.bentler.mplus"]]$df, digits = 0)+1`$*df$ the lack of good fit might have been due to the underlying assumption of multivariate normality [@Hu1999; @Schumacker2010], which was violated here.
This also held true for the CFI of `r round(fit2_summ[["FIT"]][["cfi.robust"]], digits = 2)`, the SRMR of `r round(fit2_summ[["FIT"]][["srmr"]], digits = 2)`, and the RMSEA of `r round(fit2_summ[["FIT"]][["rmsea.robust"]], digits = 2)`, 95% $CI$ [`r round(fit2_summ[["FIT"]][["rmsea.ci.lower.robust"]], digits = 2)`,`r round(fit2_summ[["FIT"]][["rmsea.ci.upper.robust"]], digits = 2)`].
Overall, the fit indices did not support the proposed model, and not all proposed paths were significant.
NFC showed no direct association with the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "c"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "c"], digits = 3)`), even though it was negatively correlated with the sum score and all subscales.
Instead, NFC showed indirect negative associations with the MBI score via lower scores in the latent variable DTH ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect1"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect1"], digits = 3)`) and via higher scores in the latent variable DRF ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "Indirect3"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "Indirect3"], digits = 3)`).
The latent variable DTL was neither related to NFC ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "a2"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "a2"], digits = 3)`) nor to the MBI score ($\beta = $`r round(fit2_summ$PE$std.all[fit2_summ$PE$label == "b2"], digits = 2)`, $p = $`r round(fit2_summ$PE$pvalue[fit2_summ$PE$label == "b2"], digits = 3)`).
